### 2019-10-30 Paper_shortened_pdf.Rmd
Reviewer 2 Comment 16 17
Updates

abstract: |
  The question whether fathers and mothers play similar roles in children’s
  emotional adjustment has been approached differently in different research
  traditions: Developmental psychologists have focused on qualitative parenting,
  and sociologists have focused on quantitative child care involvement. This
  longitudinal study (N = 1884, age 6-12) bridges these approaches, 
  investigating qualitative and quantitative involvement, and their interaction,
  in relation to emotional adjustment. On average, evidence for mothers'
  and fathers' unique roles was limited.
  When both parents were more involved, both engaged
  more in desirable qualitative parenting. When mothers were disproportionately
  involved, however, parenting roles were more differentiated:
  Fathers displayed less
  desirable qualitative parenting, and children were less well-adjusted.
  This suggests that all family members benefit from a more equal
  childcare distribution.

@@

```{r load_packages, include = FALSE}
library("papaja")
library(motley)
source("rfunctions.R")
load("results.RData")
load("table_coefficients.RData")
mask <- TRUE
masked <- function(text){
  ifelse(mask, "[masked]", text)
}
```

@@

Our target sample consisted of 1884 native `r masked("Australian")`, non-minority, intact, biological families. At the first wave, children were approximately 6 years old, $M = 6.28$, $SD = .45$, and 12 at the final wave ($M = 12.42$, $SD = .49$); on agerage, mothers were 34.89 ($SD = 4.71$), and fathers 36.94 ($SD = 5.48$). Most families were dual-earner families, based on income from wages or enterprise ($N = 1067$); the remainder were single-earner families($N = 669$ father-only, $N = 41$ mother-only). The modal annual income for fathers was between \$26,000-\$51,999 ($N = 663$ fathers reported this value), and for mothers, \$25,999 or less per year ($N = 1152$ reported this value).

@@

We calculated mean scores for all of the study variables. Scale descriptive statistics are provided in Supplementary Table 1, and scale correlations are provided in Supplementary Table 2. We deemed it defensible to assume metric measurement invariance (i.e., to assume that the factor loadings of each construct are the same across time points), as the difference in fit between structurally invariant models, and metrically invariant models, was smaller than .01 on all conventional fit indices: RMSEA, CFI, and TLI (see Supplementary Table 3).

To address our research questions, we used multilevel, autoregressive structural equation modeling [@asparouhovDynamicStructuralEquation2018]. In this approach, the variance in qualitative parenting behaviors and emotional adjustment is partialized into stable between-individual differences (the mean level for that individual across all measurement occasions), and within-individual fluctuations (deviations from this person-specific mean). This has several advantages: First, controlling for stable between-family differences allows us to estimate the direction of within-family effects more accurately [@hamakerCritiqueCrosslaggedPanel2015]. Any stable factors which might bias cross-lagged effects - such as the influence of SES or neighborhood effects - are accounted for at the between level, and reflected in the correlations between the random intercepts. Secondly, this approach enables us to directly test our hypothesis that between-family differences in quantitative involvement moderate the interplay between qualitative involvement and emotional adjustment: Between-family differences in the interplay between qualitative parenting behaviors and emotional adjustment are estimated as random effects, and we can include between-family level moderators as predictors of these random effects. In this way, we included total joint childcare, the childcare distribution, and child sex as moderators.

All analyses were conducted using Mplus 8.0 and the R-package MplusAutomation. This type of multilevel autoregressive model can only be estimated using Bayesian methods. We used two Gibbs-sampler chains of 50000 iterations each. We applied mildly informative inverse Wishart priors to the variance/covariance matrices, and normal priors centered on zero for all regression coefficients. We assessed convergence through visual inspections of the chains and posterior distributions. We report the posterior median, and a 95% highest posterior density interval (HPDI). This is the "narrowest" possible interval that contains 95% of samples from the posterior distribution. It represents the most likely population values of the parameter in question. Results are best interpreted by examining the effect size (standardized regression coefficients and correlations), and the width of the HPDI. Significance is not a Bayesian concept, but we use the shorthand "significant" to refer to estimates for which less than 5% of the posterior distribution had the opposite sign from the estimate. All standardized and unstandardized model parameters are reported in Supplementary Table 4.

>>>>

abstract: |
  The question of whether fathers and mothers play similar roles in children’s
  emotional adjustment has been approached differently in different research
  traditions: Developmental psychologists have focused on qualitative parenting,
  and sociologists have focused on quantitative child care involvement. This
  longitudinal study (N = 1884, age 6-12) bridges these approaches, 
  investigating qualitative and quantitative involvement, and their interaction,
  in relation to emotional adjustment. On average, evidence for mothers'
  and fathers' unique roles was limited.
  When both parents were more involved, both engaged
  more in desirable qualitative parenting. When mothers were disproportionately
  involved, however, parenting roles were more differentiated:
  Fathers displayed less
  desirable qualitative parenting, and children were less well-adjusted.
  This suggests that all family members benefit from a more equal
  childcare distribution.

@@

```{r load_packages, include = FALSE}
library("papaja")
library(motley)
source("rfunctions.R")
load("results.RData")
load("table_coefficients.RData")
mask <- FALSE
masked <- function(text){
  ifelse(mask, "[masked]", text)
}
```

@@

Our target sample consisted of 1884 native `r masked("Australian")`, non-minority, intact, biological families. At the first wave, children were approximately 6 years old, $M = 6.28$, $SD = .45$, and 12 at the final wave ($M = 12.42$, $SD = .49$); on agerage, mothers were 34.89 ($SD = 4.71$), and fathers 36.94 ($SD = 5.48$). Most families were dual-earner families, based on income from wages or enterprise ($N = 1067$); the remainder were single-earner families($N = 669$ father-only, $N = 41$ mother-only). Income was recorded in ordered categories. The modal annual income for fathers was between \$26,000-\$51,999 ($N = 663$ fathers reported this value), and for mothers, \$25,999 or less per year ($N = 1152$ reported this value).

@@

We calculated mean scores for all of the study variables. Scale descriptive statistics, number of items, number of complete cases, and reliability are reported in Supplementary Table 1, and scale correlations are provided in Supplementary Table 2. We deemed it defensible to assume metric measurement invariance (i.e., to assume that the factor loadings of each construct are the same across time points and respondents), as the difference in fit between structurally invariant models, and metrically invariant models, was smaller than .01 on all conventional fit indices: RMSEA, CFI, and TLI (see Supplementary Table 3).

To address our research questions, we used multilevel, autoregressive structural equation modeling [@asparouhovDynamicStructuralEquation2018]. In this approach, the variance in qualitative parenting behaviors and emotional adjustment is partialized into stable between-individual differences (the mean level for that individual across all measurement occasions), and within-individual fluctuations (deviations from this person-specific mean). This has several advantages: First, controlling for stable between-family differences allows us to estimate the direction of within-family effects more accurately [@hamakerCritiqueCrosslaggedPanel2015]. Any stable factors which might bias cross-lagged effects - such as the influence of SES or neighborhood effects - are accounted for at the between level, and reflected in the correlations between the random intercepts. Secondly, this approach enables us to directly test our hypothesis that between-family differences in quantitative involvement moderate the interplay between qualitative involvement and emotional adjustment: Between-family differences in the interplay between qualitative parenting behaviors and emotional adjustment are estimated as random effects, and we can include between-family level moderators as predictors of these random effects. In this way, we included total joint childcare, the childcare distribution, and child sex as moderators. We conducted separate analyses for the four qualitative parenting dimensions, because a model including all four variables at once was too complex to estimate.

All analyses were conducted using Mplus 8.0 and the R-package MplusAutomation. This type of multilevel autoregressive model can only be estimated using Bayesian methods. We used two Gibbs-sampler chains of 50000 iterations each. Bayes is a full-information estimator, which means that all available information is used without imputing missing values, and consistent estimation is guaranteed under the assumption that data are missing at random. The missing data handling is likelihood based and guarantees consistent estimation as long as the missing data is missing at random (MAR). We applied mildly informative inverse Wishart priors to the variance/covariance matrices, and normal priors centered on zero for all regression coefficients. We assessed convergence through visual inspections of the chains and posterior distributions. We report the posterior median, and a 95% highest posterior density interval (HPDI). This is the "narrowest" possible interval that contains 95% of samples from the posterior distribution. It represents the most likely population values of the parameter in question. Results are best interpreted by examining the effect size (standardized regression coefficients and correlations), and the width of the HPDI. Significance is not a Bayesian concept, but we use the shorthand "significant" to refer to estimates for which less than 5% of the posterior distribution had the opposite sign from the estimate. All standardized and unstandardized model parameters are reported in Supplementary Table 4.
